---
title: "Dynamics of Youth"
subtitle: "Data Factsheets"
author: "Neha Moopen<br>Utrecht University Library"
format: html
---

Dynamics of Youth has the ambition to make all data within the strategic theme as FAIR as possible. To help with this, we are creating an inventory of all projects conducted within the UU and UMCU that examine topics related to child and youth development and (mental) health. 

Are you involved in such a project? Please help us improve this overview by filling out this form! Qualtrics survey; [https://survey.uu.nl/jfe/form/SV_23nEYHwKB4i0p8i](https://survey.uu.nl/jfe/form/SV_23nEYHwKB4i0p8i)

```{r echo=FALSE, message=FALSE}
library(readr)
library(dplyr)
library(reactable)
library(htmltools)

data <- read_csv2("../data/factsheet_data_2024-01-24.csv")

data <- rename(data, 
               "project_name" = `1 `,
               "project_abbreviation" = `2 `,
               "description" = `5 `,
               "institution" = `3 _1`,
               "author" = `4 _4`,
               "design" = `9 `)

data <- filter_at(data, vars("project_name", "project_abbreviation", "description", "institution", "author", "design"), ~!is.na(.))

data <- select(data, "project_name", "project_abbreviation", "description", "institution", "author", "design")
```

```{r echo=FALSE}
row_details <- function(index) {
  project <- data[index, ]
  
  project_field <- function(name, ...) {
    if (any(is.na(...))) NULL
    else tagList(div(class = "detail-label", name), ...)
  }
  
  detail <- div(
    class = "project-detail",
    div(class = "detail-header", project$project_name),
    div(class = "detail-abbreviation", project$project_abbreviation),
    project_field("Description", project$description),
    project_field("Institution", project$institution),
    project_field("Author", project$author),
    project_field("Research Design", project$design)
  )
}
  
tbl <- reactable(
  data[, c("project_name", "project_abbreviation")],
  onClick = "expand",
  details = row_details,
  theme = reactableTheme(cellPadding = "8px 12px")
)
```

```{r echo=FALSE}
tags$link(href = "https://fonts.googleapis.com/css?family=Nunito:400,600,700&display=fallback", rel = "stylesheet")
```

```{css echo=FALSE}
.project-detail {
  font-family: Nunito, "Helvetica Neue", Helvetica, Arial, sans-serif;
  padding: 24px;
  box-shadow: inset 0 1px 3px #dbdbdb;
  background: hsl(213, 20%, 99%);
  border-radius: 4px;
}

.detail-label {
  margin: 1.25rem 0 0.25rem;
  font-size: 0.875rem;
  color: rgba(0, 0, 0, 0.6);
}

.detail-header {
  margin-bottom: 1rem;
  font-size: 1.25rem;
  font-weight: 600;
}

.detail-title {
  margin-left: 1rem;
  font-size: 0.875rem;
  font-weight: 400;
  color: rgba(0, 0, 0, 0.6);
}

.detail-description {
  font-size: 0.875rem;
}

.project-table {
  margin-top: 1rem;
  font-size: 0.9375rem;
  border: 1px solid hsl(213, 33%, 93%);
  border-radius: 4px;
  box-shadow: 0 4px 8px 0 rgba(0, 0, 0, 0.1);
}

.header {
  background-color: hsl(213, 45%, 97%);
  border-bottom-color: hsl(213, 33%, 93%);
  border-bottom-width: 1px;
  color: hsl(213, 13%, 33%);
}

.header[aria-sort]:hover,
.header[aria-sort]:focus {
  color: hsl(213, 55%, 50%);
}

.row-style {
  cursor: pointer;
}
```


```{r echo=FALSE}
tbl
```
